rfna
====

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE
)
```

[![Build Status](https://travis-ci.org/sckott/rfna.svg?branch=master)](https://travis-ci.org/sckott/rfna) [![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)


This set of functions scrapes web content, and allows searches of the content, on the eFloras website, including Flora of North America, etc.

The website: <http://www.efloras.org>

## Installation

Install `rfna`

```{r eval=FALSE}
remotes::install_github("sckott/rfna")
```

```{r}
library('rfna')
```

## Usage

Get families

```{r}
res <- get_families("fna")
res$names[1:10]
```

Get genera

```{r}
res <- get_genera(from='fna', family='Asteraceae')
res$names[1:10]
```

Parse a page

```{r}
pg1<-'http://www.efloras.org/browse.aspx?flora_id=1&start_taxon_id=10074&page=1'
head(parse_page(pg1))
```

Get state (paleate or epaleate) of receptacle.

```{r}
url <- 'http://www.efloras.org/florataxon.aspx?flora_id=1&taxon_id=102552'
receptacle(url)
```

## Meta

* Please [report any issues or bugs](https://github.com/sckott/rfna/issues)
* License: MIT
* Get citation information for `rfna` in R doing `citation(package = 'rfna')`
